Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-18 ICLR25/formula.tex
update formula.tex

For nodes $c$ in the layer between $a$ and $b$, according to the LP solution, we may check $v(c)$ is positive or negative, that will be the following definition.

\begin{definition} \label{2layer}
	Suppose we have a fixed target node $a$ and a fixed source node $b$ in two layers before $a$. Let $\UB,\LB$ be the function of precomputed upper and lower bound before the layer of $a$, and let $v$ be the function of values of nodes in the LP solution of upper bound of $a$. 
	To compute the improvement of of upper bound of $a$ by $b$, we define the following function for nodes $c$ in one layer before $a$:
	\begin{align}
		k(c) =
		\begin{cases}
			1, & \text{if } v(c) > 0 \text{ and } W_{ca} < 0\\
			0, & \text{if } v(c) \leq 0 \text{ and } W_{ca} < 0\\
			\frac{\UB(c)}{\UB(c)-\LB(c)}, & \text{if }W_{ca} > 0
		\end{cases}
	\end{align} 
\end{definition}

@@

\begin{definition}
	Continue the assumption in Definition \ref{2layer} To compute the improvement of of upper bound of $a$ by $b$, we define a distance function $D$:
	\begin{align}
		&D(b) = \ReLU(v(b))-v(\hat{b})\\
			&D(c) =
		\begin{cases}
			\max(\LB(c), 0, v(c)+D(b)k(c)W_{bc})-v(\hat{c}), & \text{if }W_{ca} < 0\\
			\min(\UB(c), v(\hat{c})+D(b)k(c)W_{bc})-v(\hat{c}), & \text{if }  W_{ca} > 0
		\end{cases}\\
		&D(a) = \sum_c D(c)W_{ca}
	\end{align}
\end{definition}

@@

	To compute $D(d)$ for nodes $d$ in one layer before $a$, we define 
	\begin{align}
		&w_0 = \sum_c D(c)W_{cd}\\
		&w_1 = \min(\UB(d),v(d)+w_0)\\		
		&D(d) =
		\begin{cases}
			w_1-v({d}), & \text{if }W_{da} > 0 \text{ and } \LB(d)\geq 0\\
		k(d)(w_1-v({d})), & \text{if }W_{da} > 0 \text{ and } \LB(d)< 0\\
		\ReLU(w_1)-v(\hat{d})	, & \text{if }  W_{da} < 0
		\end{cases}\\
		&D(a) = \sum_c D(d)W_{da}
	\end{align}
\end{definition} $-D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$.  For the lower bound, we can compute $D(a)$ by the same formula with the $v$ for lower bound LP solution and negative weights  instead.

>>>>

For nodes $c$ in the layer between $a$ and $b$, according to the LP solution, we may check $v(c)$ is positive or negative, which is the following definition.

\begin{definition} \label{2layer}
	Suppose we have a fixed target node $a$, and a fixed source node $b$ in two layers before $a$. Let $\UB,\LB$ be the function of precomputed upper and lower bound before the layer of $a$, and let $v$ be the function of values of nodes in the LP solution of upper bound of $a$. 
	To compute the improvement of of upper bound of $a$ by $b$, we define the following function $k$ for nodes $c$ in one layer before $a$:
	\begin{align}
		k(c) =
		\begin{cases}
			1, & \text{if } v(c) > 0 \text{ and } W_{ca} < 0\\
			0, & \text{if } v(c) \leq 0 \text{ and } W_{ca} < 0\\
			\frac{\UB(c)}{\UB(c)-\LB(c)}, & \text{if }W_{ca} > 0
		\end{cases}
	\end{align} 
\end{definition}

@@

\begin{definition}
	Continue the assumption in Definition \ref{2layer}. To compute the improvement of of upper bound of $a$ by $b$, we define a distance function $D$:
	\begin{align}
		&D(b) = \ReLU(v(b))-v(\hat{b})\\
			&D(c) =
		\begin{cases}
			\max(\LB(c), 0, v(c)+D(b)k(c)W_{bc})-v(\hat{c}), & \text{if }W_{ca} < 0\\
			\min(\UB(c), v(\hat{c})+D(b)k(c)W_{bc})-v(\hat{c}), & \text{if }  W_{ca} > 0
		\end{cases}\\
		&D(a) = \sum_c D(c)W_{ca}
	\end{align}
\end{definition}

@@

	To compute $D(d)$ for nodes $d$ in one layer before $a$, we define 
	\begin{align}
		&w_0 = \sum_c D(c)W_{cd}\\
		&w_1 = \min(\UB(d),v(d)+w_0)\\		
		&D(d) =
		\begin{cases}
			w_1-v({d}), & \text{if }W_{da} > 0 \text{ and } \LB(d)\geq 0\\
		k(d)(w_1-v({d})), & \text{if }W_{da} > 0 \text{ and } \LB(d)< 0\\
		\ReLU(w_1)-v(\hat{d})	, & \text{if }  W_{da} < 0
		\end{cases}\\
		&D(a) = \sum_d D(d)W_{da}
	\end{align}
\end{definition} $-D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$.  For the lower bound, we can compute $D(a)$ by the same formula with the $v$ for lower bound LP solution and negative weights  instead.
